---
title: Chinook Salmon Bycatch Status
author: Sea State 
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  pdf_document:
    fig_caption: true
fontsize: 10pt
geometry: margin=0.75in
fig.env: graphicx
---

```{r global_options, include=FALSE, warning=FALSE, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(fig.width=7.0, fig.height=2.0, fig.path='Figs/',
                      echo=FALSE, warning=FALSE, message=FALSE)
library(pander)
library(scales)
library(tidyverse)

	panderOptions('digits', 2)
  panderOptions('round', 0)
  panderOptions('keep.trailing.zeros', TRUE)
  panderOptions('big.mark', ",")
  panderOptions('keep.line.breaks', TRUE)

```


```{r,runScripts}
  # Table with allocations & year to date catch
  
  # Find vessel associated with each company
  t1 <- tmp %>% filter(Company == company)

  t2 <- tmp %>% 
        dplyr::filter(Vessel %in% t1$Vessel) %>%
        dplyr::select(Company,Vessel,ChinookRateYtd:ChinookRateHardCap,
                      PollockCatchYtd:ChinookCatchYtd,
                      ChinookBalance,PollockBalance)


  # print(as.character(QH))

  AFA <- t2 %>% filter(grepl("AFA",Company)) %>% dplyr::select(-Company)
  CDQ <- t2 %>% filter(grepl("CDQ",Company)) %>%
          separate(Company,into=c("Type","Group"))
```



The company bycatch rate to date for all AFA-hauls combined is
`r  t2 %>% 
    dplyr::filter(grepl("AFA",Company)) %>%
    dplyr::summarise(sum(ChinookCatchYtd)/sum(PollockCatchYtd)) %>%
    round(3)
`.

The company bycatch rate to date for all CDQ-hauls combined is
`r  t2 %>% 
    dplyr::filter(grepl("CDQ",Company)) %>%
    dplyr::summarise(sum(ChinookCatchYtd)/sum(PollockCatchYtd)) %>%
    round(3)
`.

<!-- The company bycatch rate (**including CDQ**) must stay under  -->
The company bycatch rate for PCC chinook must stay under 
`r  
  tmp %>% ungroup() %>%
      dplyr::filter(grepl("AFA",Company),Company==company) %>%
      dplyr::summarise((sum(ChinookBalance))/ sum(PollockBalance)) %>%
      round(3)
` to avoid exceeding the current A-season threshold allocations given to Sea State.
<!-- to avoid exceeding the current A-season Chinook allocation. -->


The company bycatch rate company must stay under
`r  tmp %>% 
      dplyr::filter(grepl("AFA",Company)) %>%
      dplyr::group_by(Company) %>% 
      dplyr::summarise(ChinookBalance=sum(ChinookBalance),PollockBalance=sum(PollockBalance)) %>% 
      # dplyr::left_join(UnassignedAllocationTable,by=c("Company"="QuotaHolder")) %>%
      dplyr::left_join(UnassignedChinook_A,by=c("Company"="QuotaHolder")) %>%
      dplyr::filter(Company == company) %>%
      dplyr::summarise(CompanyRate = sum(ChinookBalance + Unassigned)/sum(PollockBalance) )%>%
      round(3)
` to avoid exceeding current A-season PCC hard cap Chinook allocation (theshold allocations to vessels plus unassigned Chinook).


Bycatch rate for PCC fish for the last 5 day period:
`r Pcc5DayRate %>% round(3)`


<!-- Table for the AFA hauls -->

```{r,AfaCatchAndBalance}
TBL1 <- AFA  %>% 
  dplyr::select( Vessel,
                'Pollock\ncatch' = PollockCatchYtd,
                'Pollock\nbalance' = PollockBalance,
                'Chinook\ncatch' = ChinookCatchYtd,
                'Chinook\nbalance' = ChinookBalance,
                'Ytd\nrate'=ChinookRateYtd,
                'Threshold\nrate'=ChinookRateThreshold)
                #'\n Hard cap'=ChinookRateHardCap )


pander(TBL1,caption="AFA A-season Pollock catch & balance remaining (mt), Chinook catch & remaining balance, year-to-date Chinook bycatch rates, and the threshold rate required to finish the A-season.")
```



<!-- For the CDQ hauls. -->

```{r,CdqRates}
  TBL2 <- CDQ %>% 
          dplyr::select( Group,Vessel,
                      'Pollock\ncatch' = PollockCatchYtd,
                      'Pollock\nbalance' = PollockBalance,
                      'Chinook\ncatch' = ChinookCatchYtd,
                      'Chinook\nbalance' = ChinookBalance,
                      'Ytd\nrate'=ChinookRateYtd,
                      'Threshold\nrate'=ChinookRateThreshold)

  pander(TBL2,caption="CDQ A-season totals and Chinook bycatch rates for each Vessel's CDQ association.")
```

***

Note the **threshold rate** is defined the rate from here on that you have to stay under to avoid exceeding threshold allocation.

<!-- Time series of the Chinook rates for hauls by each vessel. -->

```{r,plotRates}
  # cat("Trends in Vessel rates for ",QH)
  # print(head(AHT))
  p1 <- AHT %>% 
        dplyr::filter(ManagementProgram == company) %>% 
        ggplot(aes(HaulDate,Rate)) + geom_point() + geom_smooth() + facet_wrap(~Vessel,scales="free_x") + labs(x="Date",y="Chinook rate (n/mt)")

  # print(p1 + theme_bw(10) + theme(legend.position = "top"))

```













